    \documentclass{article}

% Language setting
% Replace `english' with e.g. `spanish' to change the document language
\usepackage[english]{babel}

% Set page size and margins
% Replace `letterpaper' with `a4paper' for UK/EU standard size
\usepackage[letterpaper,top=2cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}

% Useful packages
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}

\title{PS 1}
\author{Anais Ouedraogo}

\begin{document}
\maketitle

\section{Summary}
When I was in high school, I used to help my mother keep up with her business inventory. I enjoyed entering the different products and their information in an excel sheet and trying to find out which product was the most purchased and which one brought more profit. This made me realize that I love collecting, cleaning, manipulating, and finally getting inside from data. Back in the day, I used to do it manually, now with the different data science tools everything became much easier. This passion for data drove me towards pursuing a career in data science where my desire to take this class comes from. I became even more interested in data with the coming of machine learning and artificial intelligence. In addition, I am very interested in my country's economy which is what brought me into majoring in Economics. I believe that a mix of economics and data science will be the perfect knowledge I will need to understand my country's economy and get information from the data that would help me make informed decisions when I start getting into politics.
I enrolled in this class because I wanted to deepen my knowledge of tools used by data scientists. In addition, I wanted to understand Economics in relation to data science. My plan in this class is to become perfect in R. I did R before but I still believe that there are much more things that I need to learn in R. In addition, I like how this class touches on Julia and Python. I never heard of Julia before this class and I am very excited to learn about it.
As far as the project in this class, I am not sure of what I would want to do yet but I believe I will analyze some Amazon or Netflix data.
After graduation, I would like to work as a data scientist and potentially evolve to become a data engineer which is my ultimate goal.

\section{Equation}

\[a^2+b^2=c^2\]

\end{document}
    
